\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{ragged2e}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\keyItem}[1]{
  \item {
      {#1 \vspace{-2pt}}
  }
}

\newcommand{\keyResultItem}[2]{
  \item {
    {#1 \vspace{-2pt}}
    \begin{itemize}
      \item {#2 \vspace{-2pt}}
    \end{itemize}
  }
}

\newcommand{\justifyText}[1]{
  \justifying{#1 \vspace{-2pt}}
}

% Just in case someone needs a heading that does not need to be in a list
\newcommand{\resumeHeading}[4]{
    \begin{tabular*}{0.99\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{http://vincent.fishboneapps.com/}{\Large Ting-Hsuan (Vincent) Wang}} & Email : \href{mailto:twang43@syr.edu}{twang43@syr.edu} \\
  \href{https://www.linkedin.com/in/twang443/}{https://www.linkedin.com/in/twang443} & Mobile : \href{tel:+13152438875}{+1-315-243-8875} \\
\end{tabular*}

%-----------Summary-----------------
\section{Summary}
\justifyText{The intersection of technology and social good is my passion. Coming with 5 years of professional Software Development experience at many companies, I have a verifiable history of contributing directly to company growth and expansion throughout my career. Also, I have worked for many different countries enterprises, the English Literature background led me fit in multi-culture teams quickly. Currently, I'm seeking summer intern opportunity to utilize my skills and abilities in a value-driven company that offers professional growth.}

%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
    {Syracuse University}{Syracuse, NY}
    {Master of Science in Computer Science}{Dec 2023}
    \resumeSubheading
    {Asia University}{Taichung, Taiwan}
    {Bachelor of Arts in Foreign Languages and Literature}{Jun 2016}
  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {$IC^3$ Network}{Paris, France (Remote)}
      {Senior Software Engineer}{Jan 2022 - Present}
      \resumeItemListStart
        \keyResultItem{Designed and implemented a microservice with Go and Kubernetes.}{Validate store profiles against schemas and provides API for later aggregation. Validating more than 10K store profiles.}
        \keyResultItem{Examined company search API response time implemented with the full-text search mechanism in MongoDB, and combined it with Elasticsearch to rewrite the implementation in Go.}{Increasing the speed \textbf{by 53\%}.}
        \keyResultItem{Architected a continuous build-test-deployment (CI/CD) system using GitHub Actions to support weekly releases and out-of-cycle releases.}{Increasing development efficiency \textbf{by 30\%}.}
        \keyResultItem{Added newman E2E tests, make sure the service works as expected. If not, rollback automatically.}{Keeping the services online with \textbf{99.99\%} availability.}
      \resumeItemListEnd

    \resumeSubheading
      {Dotech Technology Co., Ltd}{Taichung, Taiwan}
      {Senior Software Engineer}{Sep 2020 - Nov 2021}
      \resumeItemListStart
        \keyResultItem{Moved the services from DigitalOcean to AWS and connected the ERP central system with SAP by using RFC(remote function call). Also, we cooperated with Korean engineers and added a BI module in ERP for beverage shops.}{Increased company's revenue \textbf{by 20\%} that year.}
        \keyResultItem{Led a team with a frontend engineer and two backend engineers to develop the Project Tracking System, and I imported OKR concept into this system.}{Increasing the numbers of features and bug fixed \textbf{by 70\%}.}
        \keyResultItem{Led a team with a designer and a programmer to upgrade company's official website and related design document.}{Successfully attracted \textbf{2 large companies} to sign the contract.}
      \resumeItemListEnd

    \resumeSubheading
      {Shanghai Pu-Yu Software Development Co., Ltd}{Shanghai, China}
      {Project Manager}{Nov 2018 - Mar. 2020}
      \resumeItemListStart
        \item{Led 5 people to integrate Ordering system and storage system with ERP system. As a leader, I made a detailed and particular schedule for the timeline and endeavored to users’ demands mining. Provided technical supports in functional continuous iteration and upgrading.}
        \item{Built a complete online to offline (O2O) ordering system and docked with store POS system, multiple delivery and payment companies.}
      \resumeItemListEnd

% --------Multiple Positions Heading------------
    \resumeSubSubheading
     {Junior PHP Engineer}{Aug 2017 - Oct 2018}
     \resumeItemListStart
        \item{Modernized FitnessFactory's official website and made a complete CMS with Laravel framework.}
     \resumeItemListEnd
%-------------------------------------------

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeSubItem{Vincent's Corner\href{https://vincent.fishboneapps.com/}{(\underline{Link})}}
      {Recorded my learning about programming in over 100 articles since 2016. The website is made by Hexo.}
    \resumeSubItem{Asia University Extracurricular Activities \& Service Learning Group Website\href{https://sls.asia.edu.tw/}{(\underline{Link1}, }\href{https://elective.easls.asia/}{\underline{Link2})}}
      {}
      \resumeItemListStart
        \keyItem{Created a website, Link1, which has attracted over \textbf{1,000,000 page views}.}
        \keyResultItem{Created a website, Link2, which allows students to select extracurricular activities.}{Supports \textbf{3,000} students to select their curriculums online at the same time.}
        \keyItem{Maintain both of sites since \textbf{2014}.}
        \keyItem{Collaborate with \textbf{faculty and university administrators}.}
      \resumeItemListEnd
    \resumeSubItem{GladLess Online E-commerce\href{https://gladless.com/}{(\underline{Link})}}
      {Using Laravel to build the complete functions for E-commerce. There are two platforms for user and manager respectively. Management platform includes permission management, merchandise management, SKU management, order management, storage management. User platform includes shopping cart, order, payment, review, refund, coupon.}
    \resumeSubItem{Member System\href{https://member.tatcmf.org.tw/}{(\underline{Link})}}
      {Using Laravel to build the membership system. The administrator can manage all members information with only one website.}
  \resumeSubHeadingListEnd


%--------PROGRAMMING SKILLS------------
\section{Programming Skills}
  \resumeSubHeadingListStart
    \keyItem{\textbf{Domains}}
      \resumeItemListStart
        \keyItem{Git, Github Action(CI/CD), Linux, Backend Engineering, Software Development, REST APIs}
      \resumeItemListEnd
    \keyItem{\textbf{Backend}}
      \resumeItemListStart
        \keyItem{Languages: PHP, Go, Java, JavaScript, SQL, NoSQL, C/C++}
        \keyItem{Frameworks: Laravel, WordPress, gin, Hexo}
        \keyItem{Tools: ORMs, Swagger, Postman, ElasticSearch}
        \keyItem{Database: MySQL, MariaDB, PostgreSQL, MongoDB, Redis}
        \keyItem{DevOps: Docker, Kubernetes, LNMP, DigitalOcean, Alibaba Cloud, AWS}
      \resumeItemListEnd
    \keyItem{\textbf{Frontend}}
      \resumeItemListStart
        \keyItem{Languages: HTML, CSS, jQuery}
        \keyItem{Tools: Webpack, ESLint, Package Manager(npm, yarn)}
      \resumeItemListEnd
    \keyItem{\textbf{Miscellaneous}}
      \resumeItemListStart
        \keyItem{Payment Flow API: WeChat Pay, Alipay, Line Pay, Third-Party Pay}
        \keyItem{Logistics API: SF Express, 7-Eleven}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%--------HONORS & AWARDS------------
\section{HONORS \& AWARDS}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Outstanding Achievement Award (Technology R\&D Project)}{School Level}
      {}{Mar. 2015}
    \resumeSubheading
      {Excellent Work Award of the 8th Dunhuang National College Cup}{National Level}
      {Advanced University Group}{May. 2014}
  \resumeSubHeadingListEnd

%-------------------------------------------
\end{document}
